### 2014-09-15 PrivacyProtection-2014-09-09.tex
Adding structure
finished description of it-systems

\textbf{Description:}
A \textit{Citizen (a)} carries a mobile device running the \textit{Sensor Collector (d)} application.
The \textit{Sensor Collector} application collects sensor data (accelerometer, GPS, GSM, ...) and sends it to the \textit{Data Cetner (c)}. 
The \textit{Data Center} on the other side sends beneficial information (traffic jam reports, bus schedule) for \textit{Citizens} to the mobile device.
The \textit{System Provider (b)} provides and operates technical infrastructure like the Data Center and the \textit{Report Tool (f)}.
The \textit{Report Tool} queries the \textit{Data Center} for aggregated data to visualize in form of charts and other means suitable to help understanding of monitored \textit{Citizens}. 
\textit{Local Authorities (c)} use the \textit{Report Tool} to get information in order to understand citizen movement and improve public services.

In such systems, the most valuable information is not the raw sensor data, the beneficial information for \textit{Local Authorities} is produced via \textit{Data Mining}.

\textbf{In this
scenario the mobile the server conducts data mining on aggregated user
data and additionally trys to combine it with publicly accessible data
to enhance the results.}

When no connection to the L+G servers is available, the mining
end-products are stored on the mobile device.

>>>>

A \textit{Citizen (a)} carries a mobile device running the \textit{Sensor Collector (d)} application.
The \textit{Sensor Collector} application collects sensor data (accelerometer, GPS, GSM, ...) and sends it to the \textit{Data Cetner (c)}. 
The \textit{Data Center} on the other side sends beneficial information (traffic jam reports, bus schedule) for \textit{Citizens} to the mobile device.
The \textit{System Provider (b)} provides and operates technical infrastructure like the Data Center and the \textit{Report Tool (f)}.
The \textit{Report Tool} queries the \textit{Data Center} for aggregated data to visualize in form of charts and other means suitable to help understanding of monitored \textit{Citizens}. 
\textit{Local Authorities (c)} use the \textit{Report Tool} to get information in order to understand citizen movement and improve public services.

In such systems, the most valuable information is not the raw sensor data, the beneficial information for \textit{Local Authorities} is produced via \textit{Data Mining} (Human Activity Recognition: detect running, walking, standing, ...). 
Usually, \textit{Data Mining} is heavily conduct within the \textit{Data Center}, but simpler mining processes can also be conducted on mobile devices.
